\iffalse
  \title{Permutations And Combinations}
  \author{BALAJI B}
  \section{subjective}
\fi

    \item   Five balls of different colours are to be placed in three boxes of different size. Each box can hold all five. In how many different ways can we place the balls so that no balls remain empty?\hfill (1981- 4 \text{ Marks})
    
    \item $m$ men and $n$ women are seated in a row so that no two women sit together. If $m>n$, then show that the number of ways in which they can be seated is $\frac{m!(m+1)!}{(m-n+1)!}$ \\

    \hfill (1983-2\text{ Marks})
    \item 7 relatives of a man comprises 4 ladies and 3 gentleman; his wife also has 7 relatives; 3 of them are ladies 4 gentleman. In how many ways they invite a dinner party of 3 ladies and 3 gentlemen so that there are 3 of man's relatives and 3 of wife's relatives?
    
    \hfill (1985- 5 \text{ Marks})
    \item A box contains two white balls, three black balls and four red balls. In how many ways can three balls be drawn from the box if at least one black ball is to be included in the draw?\hfill (1986-2\text{ Marks})
    
    \item Eighteen guests have to be seated, half on each side of a long table. Four particular guests desire to sit on one particular side and three others on the other side. Determine the number of ways in which the sitting arrangements can be made.\hfill (1991-4\text{ Marks})
    \item A committee of 12 is to be formed from 9 women and 8 men. .In how many ways this can be done if at least five women have to be included in a committee? In how many of these committees \hfill (1994- 4 \text{ Marks})

    (a)  The women are in majority?

    (b)  The men are in majority?
    
    \item Prove by permutation or otherwise $\frac{(n^2)!}{(n!)^n}$ is an integer $(n\in \mathbf{I}^+) $\hfill (2004-2\text{ Marks})
     \item If total number of runs scored in n matches is
     
     $\brak{\frac{n+1}{4}}$  $(2^{n+1}-n-2)$ where $n>1$, and the run scored in the $k^{th}$ match are given by $k$. $2^{n+1-k}$, where$ 1 \leq k \leq n$. Find $n$ \hfill (2005- 2 \text{ Marks})
     



