\iffalse
\title{Properties of Triangles}
\author{EE24Btech11022 - Eshan sharma}
\section{mcq-multiple}
\fi
%begin{document}
%begin{enumerate}
    \item There exists a triangle $ABC$ satisfying the conditions
    \hfill{(1986 - 2 mark)}
    \begin{enumerate}
    	\item $b\sin{A} = a, A <\pi/2$
    	\item $b\sin{A} > a, A >\pi/2$
    	\item $b\sin{A} > a, A <\pi/2$
    	\item $b\sin{A} < a, A <\pi/2$, $b > a$
    	\item $b\sin{A} < a, A >\pi/2$, $b = a$
    \end{enumerate}
    \item In a triangle, the lengths of two larger sides are $10$ and $9$ respectively. If the angles are in AP, Then length of third side is
    \hfill{(1987 - 2 mark)}
    \begin{multicols}{2}
    	\begin{enumerate}
    		\item $5-\sqrt{6}$ 
    		\item $3\sqrt{3}$
    		\item $3$
    		\item $5+\sqrt{6}$ 
    		\item none
    	\end{enumerate}
    \end{multicols}
    \item If in a triangle $PQR$, $\sin{P}, \sin{Q}, \sin{R}$ are in AP, then
    \hfill{(1998 - 2 mark)}
    \begin{enumerate}
    	\item The altitudes are in AP
    	\item The altitudes are in HP
    	\item The medians are in GP
    	\item The medians are in AP
    \end{enumerate}
    \item Let $A_{0}A_{1}A_{2}A_{3}A_{4}A_{5}$ be a regular hexagon inscribed in a circle of unit radius. Then the product of the lengths of the line segments $A_{0}A_{1}$,$A_{0}A_{2}$ and $A_{0}A_{4}$ is 
    \hfill{(1998 - 2 mark)}
    \begin{multicols}{2}
    	\begin{enumerate}
    		\item ${\frac{3}{4}}$
    		\item $3\sqrt{3}$
    		\item $3$
    		\item ${\frac{3\sqrt{3}}{2}}$
    	\end{enumerate}
    \end{multicols}
    \item In $\Delta ABC$, internal angle bisector of $\angle A$ meets side $BC$ in $\vec{D}$. $DE \perp AD$ meets $AC$ in $\vec{E}$ and $AB$ in $\vec{F}$. Then
    \hfill{(2006-5M,-1)}
    \begin{enumerate}
    	\item $AE$ is HM of $b \text{ and } c$
    	\item $AD$ = ${\frac{2bc}{b+c}}cos{\frac{A}{2}}$
    	\item $EF$ = ${\frac{4bc}{b+c}}sin{\frac{A}{2}}$
    	\item $\Delta AEF$ is isosceles
    \end{enumerate}
    \item Let $ABC$ be a triangle such that $\angle ACB = \pi/6$ and let $a,b \text{ and } c$ denote lengths of the sides opposite to $\vec{A}$,$\vec{B} \text{ and } \vec{C}$ respectively. The value(s) of $x$ for which $a = x^{2}+x+1, b = x^{2}-1, c = 2x+1$ is(are)
    \hfill{(2010)}
    \begin{multicols}{2}
    	\begin{enumerate}
    		\item $-(2+\sqrt{3})$
    		\item $1+\sqrt{3}$
    		\item $2+\sqrt{3}$
    		\item $4\sqrt{3}$
    	\end{enumerate}
    \end{multicols}
    \item In a triangle $PQR$, $\vec{P}$ is the largest angle and $\cos{P} = \frac{1}{3}$. Further the incircle of the triangle touches the sides $PQ,QR \text{ and } RP$ at $\vec{N},\vec{L} \text{ and } \vec{M}$ respectively, such that the lengths of $PN, QL \text{ and } RM$ are consecutive even integers. Then possible length(s) of the side(s) of the triangle is(are)
    \hfill{(Jee Adv. 2013)}
    \begin{multicols}{2}
    	\begin{enumerate}
    		\item $16$
    		\item $24$
    		\item $18$
    		\item $22$
    	\end{enumerate}
    \end{multicols}
    \item In a triangle $XYZ$, let $x,y,z$ be the lengths of sides opposite to angles $\vec{X},\vec{Y},\vec{Z} \text{ and } 2s = x+y+z$. If ${\frac{s-x}{4}}={\frac{s-y}{3}}={\frac{s-z}{2}}$ and area of the incircle of the triangle $XYZ$ is ${\frac{8\pi}{3}}$
    \hfill{(Jee Adv. 2016)}
    \begin{enumerate}
    	\item area of the triangle is $6\sqrt{6}$
    	\item the radius of circumcirle of $XYZ$ is ${\frac{35\sqrt{6}}{6}}$
    	\item $sin\frac{X}{2}sin\frac{Y}{2}sin\frac{Z}{2} = \frac{4}{35}$
    	\item $sin^{2}\brak{\frac{X+Y}{2}}$ = $\frac{3}{5}$
    \end{enumerate}
    \item In a triangle $PQR$, let $\angle PQR = 30\degree$ and the sides $PQ \text{ and } QR$ have lengths $10\sqrt{3}$ and $10$ respectively. Then which of the following statements is(are) TRUE?
    \hfill{(Jee Adv. 2018)}
    \begin{enumerate}
    	\item $\angle QPR = 45\degree$
    	\item the area of the triangle $PQR$ is $25\sqrt{3}$ and $\angle QRP = 120\degree$
    	\item the radius of the incircle of triangle $PQR$ is $10\sqrt{3}-15$
    	\item the radius of circumcirle $PQR$ is $100\pi$
    \end{enumerate}
    \item In a non-right-angle triangle $\Delta PQR$, let $p,q,r$ denote the lengths of the sides opposite to the angles at $\vec{P},\vec{Q},\vec{R}$ respectively. The median from $\vec{R}$ meets the side $PQ$ at $\vec{S}$, the perpendicular from $\vec{P}$ meets the side $QR$ at $\vec{E}$, $RS \text{ and } PE$ intersect at $\vec{O}$. If $p = \sqrt{3}$, $q = 1$ and the radius of the circumcircle at $\Delta PQR$ equals $1$, then which of the following options is(are)\\ correct.
    \hfill{(Jee Adv. 2018)}
    \begin{enumerate}
    	\item Radius of incircle of $\Delta PQR$ = $\frac{\sqrt{3}}{2}\brak{2-\sqrt{3}}$
    	\item Area of $\Delta SOE = \frac{\sqrt{3}}{12}$
    	\item Length of $OE = \frac{1}{6}$
    	\item Length of $RS = \frac{\sqrt{7}}{2}$
    \end{enumerate}

%end{enumerate}
%end{document}

