
\iffalse
  \title{20. Vector Algebra}
  \author{Niketh Prakash Achanta - EE24BTECH11047}
  \section{subjective}
\fi

\item From a point $\vec{O}$ inside the triangle ABC, perpendiculars OD,OE,OF are drawn to the sides BC,CA,AB respectively. Prove that the perpendiculars from $\vec{A,B,C}$ to the sides EF,FD,DE are concurrent. \hfill{\brak{1978}}\\

	\item $A_1,A_2,......A_n$ are the vertices of a regular plane polygon with n sides and $\vec{O}$ is its centre. Show that
	$\sum_{i=1}^{n-1}\brak{OA_i\times OA_{i+1}}= \brak{1-n}\brak{OA_2\times OA_1}$
		\hfill{\brak{1982-2Marks}}\\

	\item Find all values of $\lambda$ such that $x,y,z\neq\brak{0,0,0}$ and $\brak{\hat{i}+\hat{j}+3\hat{k}}x+\brak{3\hat{i}-3\hat{j}+\hat{k}}y+\brak{-4\hat{i}+5\hat{j}}z=\lambda\brak{x\hat{i}+y\hat{j}+z\hat{k}}$ where $\hat{i},\hat{j},\hat{k}$ are unit vectors along the coordinate axes. \hfill{\brak{1982-3Marks}}\\

	\item A vector $\vec{A}$ has components $A_1,A_2,A_3$ in a right-handed rectangular Cartesian coordinate system oxyz. The coordinate system is rotated about the x-axis through an angle $\frac{\pi}{2}$. Find the components of A in the new coordinate system, in terms of $A_1,A_2,A_3$. \hfill{\brak{1983-2Marks}}\\

	\item The position vectors of the points $\vec{A,B,C\ \text{and}\ D}$ are $\brak{3\hat{i}-2\hat{j}-\hat{k}}$,$\brak{2\hat{i}+3\hat{j}-4\hat{k}}$,$\brak{-\hat{i}+\hat{j}+2\hat{k}}$ and $\brak{4\hat{i}+5\hat{j}+\lambda\hat{k}}$, respectively. If the points $\vec{A,B,C\ \text{and}\ D}$ lie on a plane, find the value of $\lambda$. \hfill{\brak{1986-2.5Marks}}\\

	\item If $\vec{A,B,C,D}$ are any four points in space, prove that-
		$\abs{AB\times CD+ BC\times AD+CA\times BD}=$\\ $4$\brak{area\ of\ triangle\ ABC}  \hfill{\brak{1987-2Marks}}\\


	\item Let OACB be a parallelogram with $\vec{O}$ at the origin and OC a diagonal. Let $\vec{D}$ be the midpoint of OA. Using vector methods prove that BD and CO intersect in the same ratio. Determine this ratio. \hfill{\brak{1988-3Marks}}\\ 

\item If vectors $\vec{a},\vec{b},\vec{c}$ are coplanar, show that
	$
		\mydet {
\vec{a} & \vec{b} & \vec{c} \\
\vec{a}\cdot\vec{a} & \vec{a}\cdot\vec{b} & \vec{a}\cdot\vec{c} \\
\vec{b}\cdot\vec{a} & \vec{b}\cdot\vec{b} & \vec{b}\cdot\vec{c}
 }=\vec{0}
		$ \hfill{\brak{1989-2Marks}}\\

	\item In a triangle OAB, $\vec{E}$ is the midpoint of BO and $\vec{D}$ is a point on AB such that AD:DB=2:1. If OD and AE intersect at $\vec{P}$, determine the ratio OP:PD  using vector methods. \hfill{\brak{1989-4 Marks}}\\

	\item Let $\vec{A}=2\hat{i}+\hat{k},\vec{B}=\hat{i}+\hat{j}+\hat{k}$, and $\vec{C}=4\hat{i}-3\hat{j}+7\hat{k}$. Determine a vector $\vec{R}$ satisfying $\vec{R\times B}=\vec{C\times B}$ and $\vec{R}\cdot\vec{A}=0$ \hfill{\brak{1990-3Marks}}\\

	\item Determine the value of 'c' so that for all real $x$, the vector $cx\hat{i}-6\hat{j}-3\hat{k}$ and $x\hat{i}+2\hat{j}+2cx\hat{k}$ make an obtuse angle with each other. \hfill{\brak{1991-4Marks}}\\

	\item In a triangle ABC,$\vec{D}$ and $\vec{E}$ are points on BC and AC respectively, such that $BD=2DC$ and $AE=3EC$. Let $\vec{P}$ be the point of intersection of AD and BE. Find BP/PE using vector methods. \hfill{\brak{1993-5Marks}}\\

	\item If the vectors $\vec{b,c,d}$ are not coplanar, then prove that the vector $\vec{\brak{a\times b}\times\brak{c\times d}}+\vec{\brak{a\times c}\times\brak{d\times b}}+\vec{\brak{a\times d}\times\brak{b\times c}}$ is parallel to $\vec{a}$. \hfill{\brak{1994-4Marks}}\\

	\item The position vectors of the vertices $\vec{A,B\ \text{and}\ C}$ of a tetrahedron ABCD are $\vec{\hat{i}+\hat{j}+\hat{k},\hat{i}}$ and $\vec{3\hat{i}}$ respectively. The altitude from vertex $\vec{D}$ to the opposite face ABC meets the median line through $\vec{A}$ of the triangle ABC at a point $\vec{E}$. If the length of the side AD is $4$ and the volume of the tetrahedron is$\frac{2\sqrt{2}}{3}$, find the position vector of the point $\vec{E}$ for all its possible positions. \hfill{\brak{1996-5Marks}}
